---
title: "Awit, Julia Theressa"
output: pdf_document
date: "03-03-2025"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=TRUE)
```

#Github Link: 

5. A geospatial analysis system images. The percentage of images supplied by each censor and the percentage of images relevant to a query are shown in the following table.
```{r}
##Define the data
sensors <- data.frame(Supplied = c(15, 20, 25, 40), Relevant = c(50, 60, 80, 85))

##Compute (Overall relevance using a weighted sum)
overall_relevance <- sum((sensors$Supplied / 100) * (sensors$Relevant / 100)) * 100

##Print
cat("Overall percentage of relevant images:", overall_relevance, "%\n")
``` 
6. A fair coin is tossed twice.

Let E1 be the event that both tosses have the same outcome, that is,
E1 = (HH, TT).
Let E2 be the event that the first toss is a head, that is, E2 = (HH, HT).
Let E3 be the event that the second toss is a head, that is, E3 = (TH, HH).
Show that E1, E2, and E3 are pairwise independent but not mutually independent.
```{r}
s <- c("HH", "HT", "TH", "TT")
E1 <- c("HH", "TT"); E2 <- c("HH", "HT"); E3 <- c("HH", "TH")
P <- function(E) length(E) / length(s)
PI <- function(A, B) length(intersect(A, B)) / length(s)
PE1 <- P(E1); PE2 <- P(E2); PE3 <- P(E3)
PE1E2 <- PI(E1, E2); PE1E3 <- PI(E1, E3); PE2E3 <- PI(E2, E3)
PE1E2E3 <- PI(intersect(E1, E2), E3)

pairwise <- (PE1E2 == PE1 * PE2) & (PE1E3 == PE1 * PE3) & (PE2E3 == PE2 * PE3)
mutual <- (PE1E2E3 == PE1 * PE2 * PE3)

cat("P(E1)=", PE1, " P(E2)=", PE2, " P(E3)=", PE3, "\n")
cat("P(E1∩E2)=", PE1E2, " P(E1∩E3)=", PE1E3, " P(E2∩E3)=", PE2E3, "\n")
cat("P(E1∩E2∩E3)=", PE1E2E3, "\n")
cat("Pairwise independent?", pairwise, "\nMutually independent?", mutual, "\n")
``` 

