---
title: "FA5"
author: "Awit, Julia Theressa"
output: pdf_document
---

# Exercise 6
```{r}
# Given data
server_data <- data.frame(
  server = c("Server 1", "Server 2", "Server 3"),
  pct_messages = c(40, 25, 35) / 100,
  pct_errors = c(1, 2, 1.5) / 100
)

# (a) Probability of receiving an email with an error
p_error <- sum(server_data$pct_messages * server_data$pct_errors)

# (b) Probability of a message arriving without error
p_no_error <- 1 - p_error

# (c) Probability that a message was sent through Server 1 given it arrived without error
p_server1_given_no_error <- (server_data$pct_messages[1] * (1 - server_data$pct_errors[1])) / p_no_error

# Print results
list(p_error = round(p_error, 4), p_no_error = round(p_no_error, 4), p_server1_given_no_error = round(p_server1_given_no_error, 4))
```

# Exercise 9
```{r}
# Given probabilities
p_A <- 0.2  # Not buying
p_B <- 0.7  # Buying
p_C <- 0.1  # Undecided
p_G_given_A <- 0.1
p_G_given_B <- 0.4
p_G_given_C <- 0.2

# (a) Probability of not upgrading
p_G <- (p_A * p_G_given_A) + (p_B * p_G_given_B) + (p_C * p_G_given_C)
p_not_G <- 1 - p_G

# (b) Posterior probability of buying given G
p_B_given_G <- (p_B * p_G_given_B) / p_G

# (c) Calculating required probabilities
p_B_given_not_G <- (p_B * (1 - p_G_given_B)) / p_not_G
p_C_given_G <- (p_C * p_G_given_C) / p_G
p_C_given_not_G <- (p_C * (1 - p_G_given_C)) / p_not_G

# Print results
list(p_not_G = round(p_not_G, 4), p_B_given_G = round(p_B_given_G, 4), p_B_given_not_G = round(p_B_given_not_G, 4), p_C_given_G = round(p_C_given_G, 4), p_C_given_not_G = round(p_C_given_not_G, 4))
```

# Exercise 13
```{r}
# Given probabilities
p_I <- 0.7  # Internet
p_E <- 0.3  # Email
p_D_given_I <- 0.6  # Detected if from Internet
p_D_given_E <- 0.8  # Detected if from Email

# (a) Probability of infection (not detected)
p_not_D_given_I <- 1 - p_D_given_I
p_not_D_given_E <- 1 - p_D_given_E
p_infected <- (p_I * p_not_D_given_I) + (p_E * p_not_D_given_E)

# (b) Probability that detected spyware came from Internet
p_D <- (p_I * p_D_given_I) + (p_E * p_D_given_E)
p_I_given_D <- (p_I * p_D_given_I) / p_D

# Print results
list(p_infected = round(p_infected, 4), p_I_given_D = round(p_I_given_D, 4))
